PANCHANGE_analysis

### 2020-11-06 PANCHANGE_analysis.Rmd

Sensitivity analysis for individuals who signed up to GLAD (prepan) either 3, 6 or 9 months before the pendemic began. 
```{r subsample for pre-pan sensitivity analysis}
# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_3months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_3_months_numeric == 1 # Only participants who signed up between December 1st 2019 and March 1st 2020
  )

# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_6months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_6_months_numeric == 1 # Only participants who signed up between September 1st 2019 and March 1st 2020
  )

# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_9months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_9_months_numeric == 1 # Only participants who signed up between June 1st 2019 and March 1st 2020
  )

```

@@

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```
# GAD prepan: sensitivity
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
#### Subset of participants 3 months prior to pandemic
```{r gad model1b sum_score prepan - sensitivity 3 months}
# Regression coefficients
gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_3months")
kable(gad_prepan_model1b_explan_estimates)
gad_prepan_model1b_explan_estimates

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_3months")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```

#### Subset of participants 6 months prior to pandemic
```{r gad model1b sum_score prepan - sensitivity 6 months}
# Regression coefficients
gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_6months")
kable(gad_prepan_model1b_explan_estimates)
gad_prepan_model1b_explan_estimates

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_6months")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```

#### Subset of participants 9 months prior to pandemic
```{r gad model1b sum_score prepan - sensitivity 9 months}
# Regression coefficients
gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_9months")
kable(gad_prepan_model1b_explan_estimates)
gad_prepan_model1b_explan_estimates

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_9months")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```
##KT

@@

# Regression diagnostic statistics
phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_explan_reg_stats)
phq_prepan_model1b_explan_reg_stats
```
# PHQ prepan: sensitivity
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
#### Subset of participants 3 months prior to pandemic
```{r phq model1b sum_score prepan - sensitivity 3 months}
# Regression coefficients
phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_3months")
kable(phq_prepan_model1b_explan_estimates)
phq_prepan_model1b_explan_estimates

# Regression diagnostic statistics
phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_3months")
kable(phq_prepan_model1b_explan_reg_stats)
phq_prepan_model1b_explan_reg_stats
```

#### Subset of participants 6 months prior to pandemic
```{r phq model1b sum_score prepan - sensitivity 6 months}
# Regression coefficients
phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_6months")
kable(phq_prepan_model1b_explan_estimates)
phq_prepan_model1b_explan_estimates

# Regression diagnostic statistics
phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_6months")
kable(phq_prepan_model1b_explan_reg_stats)
phq_prepan_model1b_explan_reg_stats
```

#### Subset of participants 9 months prior to pandemic
```{r phq model1b sum_score prepan - sensitivity 9 months}
# Regression coefficients
phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_9months")
kable(phq_prepan_model1b_explan_estimates)
phq_prepan_model1b_explan_estimates

# Regression diagnostic statistics
phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_9months")
kable(phq_prepan_model1b_explan_reg_stats)
phq_prepan_model1b_explan_reg_stats
```

@@

# PCL prepan: sensitivity
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
#### Subset of participants 3 months prior to pandemic
```{r pcl model1b sum_score prepan - sensitivity 3 months}
# Regression coefficients
pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_3months")
kable(pcl_prepan_model1b_explan_estimates)
pcl_prepan_model1b_explan_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_3months")
kable(pcl_prepan_model1b_explan_reg_stats)
pcl_prepan_model1b_explan_reg_stats
```

#### Subset of participants 6 months prior to pandemic
```{r pcl model1b sum_score prepan - sensitivity 6 months}
# Regression coefficients
pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_6months")
kable(pcl_prepan_model1b_explan_estimates)
pcl_prepan_model1b_explan_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_6months")
kable(pcl_prepan_model1b_explan_reg_stats)
pcl_prepan_model1b_explan_reg_stats
```

#### Subset of participants 9 months prior to pandemic
```{r pcl model1b sum_score prepan - sensitivity 9 months}
# Regression coefficients
pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_9months")
kable(pcl_prepan_model1b_explan_estimates)
pcl_prepan_model1b_explan_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_9months")
kable(pcl_prepan_model1b_explan_reg_stats)
pcl_prepan_model1b_explan_reg_stats
```

>>>>

@@

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```

@@

# Regression diagnostic statistics
phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "phq.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_explan_reg_stats)
phq_prepan_model1b_explan_reg_stats
```

@@

# SENSITIVITY based on highest level of education

# GAD prepan
## Regression: Absolute scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r gad education sensitivity model0a sum_score prepan}
# Regression coefficients
gad_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model0a_education_estimates)
gad_prepan_model0a_education_estimates

# Regression diagnostic statistics
gad_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model0a_education_reg_stats)
gad_prepan_model0a_education_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r gad education sensitivity model0b sum_score prepan}
# Regression coefficients
gad_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model0b_education_estimates)
gad_prepan_model0b_education_estimates

# Regression diagnostic statistics
gad_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model0b_education_reg_stats)
gad_prepan_model0b_education_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad education sensitivity model1a sum_score prepan}
# Regression coefficients
gad_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1a_education_estimates)
gad_prepan_model1a_education_estimates

# Regression diagnostic statistics
gad_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1a_education_reg_stats)
gad_prepan_model1a_education_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad education sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_estimates)
gad_prepan_model1b_education_estimates

# Regression diagnostic statistics
gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_reg_stats)
gad_prepan_model1b_education_reg_stats
```

# PHQ prepan
## Regression: Absolute scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r phq education sensitivity model0a sum_score prepan}
# Regression coefficients
phq_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model0a_education_estimates)
phq_prepan_model0a_education_estimates

# Regression diagnostic statistics
phq_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model0a_education_reg_stats)
phq_prepan_model0a_education_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r phq education sensitivity model0b sum_score prepan}
# Regression coefficients
phq_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model0b_education_estimates)
phq_prepan_model0b_education_estimates

# Regression diagnostic statistics
phq_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model0b_education_reg_stats)
phq_prepan_model0b_education_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq education sensitivity model1a sum_score prepan}
# Regression coefficients
phq_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1a_education_estimates)
phq_prepan_model1a_education_estimates

# Regression diagnostic statistics
phq_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1a_education_reg_stats)
phq_prepan_model1a_education_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq education sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_estimates)
phq_prepan_model1b_education_estimates

# Regression diagnostic statistics
phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_reg_stats)
phq_prepan_model1b_education_reg_stats
```

# OCIR prepan 
## Regression: Absolute scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r ocir education sensitivity model0a sum_score prepan}
# Regression coefficients
ocir_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model0a_education_estimates)
ocir_prepan_model0a_education_estimates

# Regression diagnostic statistics
ocir_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model0a_education_reg_stats)
ocir_prepan_model0a_education_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r ocir education sensitivity model0b sum_score prepan}
# Regression coefficients
ocir_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model0b_education_estimates)
ocir_prepan_model0b_education_estimates

# Regression diagnostic statistics
ocir_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model0b_education_reg_stats)
ocir_prepan_model0b_education_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir education sensitivity model1a sum_score prepan}
# Regression coefficients
ocir_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1a_education_estimates)
ocir_prepan_model1a_education_estimates

# Regression diagnostic statistics
ocir_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1a_education_reg_stats)
ocir_prepan_model1a_education_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir education sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_estimates)
ocir_prepan_model1b_education_estimates

# Regression diagnostic statistics
ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_reg_stats)
ocir_prepan_model1b_education_reg_stats
```

#PCL prepan 
## Regression: Absolute scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r pcl education sensitivty model0a sum_score prepan}
# Regression coefficients
pcl_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model0a_education_estimates)
pcl_prepan_model0a_education_estimates

# Regression diagnostic statistics
pcl_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model0a_education_reg_stats)
pcl_prepan_model0a_education_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r pcl education sensitivty model0b sum_score prepan}
# Regression coefficients
pcl_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model0b_education_estimates)
pcl_prepan_model0b_education_estimates

# Regression diagnostic statistics
pcl_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model0b_education_reg_stats)
pcl_prepan_model0b_education_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl education sensitivty model1a sum_score prepan}
# Regression coefficients
pcl_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1a_education_estimates)
pcl_prepan_model1a_education_estimates

# Regression diagnostic statistics
pcl_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1a_education_reg_stats)
pcl_prepan_model1a_education_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl education sensitivty model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_education_estimates)
pcl_prepan_model1b_education_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_education_reg_stats)
pcl_prepan_model1b_education_reg_stats
```

# SENSITIVITY based on employment status

# GAD prepan
## Regression: Absolute scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r gad employment sensitivity model0a sum_score prepan}
# Regression coefficients
gad_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model0a_employment_estimates)
gad_prepan_model0a_employment_estimates

# Regression diagnostic statistics
gad_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model0a_employment_reg_stats)
gad_prepan_model0a_employment_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r gad employment sensitivity model0b sum_score prepan}
# Regression coefficients
gad_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model0b_employment_estimates)
gad_prepan_model0b_employment_estimates

# Regression diagnostic statistics
gad_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model0b_employment_reg_stats)
gad_prepan_model0b_employment_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment sensitivity model1a sum_score prepan}
# Regression coefficients
gad_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1a_employment_estimates)
gad_prepan_model1a_employment_estimates

# Regression diagnostic statistics
gad_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1a_employment_reg_stats)
gad_prepan_model1a_employment_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_employment_estimates)
gad_prepan_model1b_employment_estimates

# Regression diagnostic statistics
gad_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_employment_reg_stats)
gad_prepan_model1b_employment_reg_stats
```

# PHQ prepan
## Regression: Absolute scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r phq employment sensitivity model0a sum_score prepan}
# Regression coefficients
phq_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model0a_employment_estimates)
phq_prepan_model0a_employment_estimates

# Regression diagnostic statistics
phq_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model0a_employment_reg_stats)
phq_prepan_model0a_employment_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r phq employment sensitivity model0b sum_score prepan}
# Regression coefficients
phq_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model0b_employment_estimates)
phq_prepan_model0b_employment_estimates

# Regression diagnostic statistics
phq_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model0b_employment_reg_stats)
phq_prepan_model0b_employment_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment sensitivity model1a sum_score prepan}
# Regression coefficients
phq_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1a_employment_estimates)
phq_prepan_model1a_employment_estimates

# Regression diagnostic statistics
phq_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1a_employment_reg_stats)
phq_prepan_model1a_employment_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_employment_estimates)
phq_prepan_model1b_employment_estimates

# Regression diagnostic statistics
phq_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_employment_reg_stats)
phq_prepan_model1b_employment_reg_stats
```

# OCIR prepan 
## Regression: Absolute scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r ocir employment sensitivity model0a sum_score prepan}
# Regression coefficients
ocir_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model0a_employment_estimates)
ocir_prepan_model0a_employment_estimates

# Regression diagnostic statistics
ocir_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model0a_employment_reg_stats)
ocir_prepan_model0a_employment_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r ocir employment sensitivity model0b sum_score prepan}
# Regression coefficients
ocir_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model0b_employment_estimates)
ocir_prepan_model0b_employment_estimates

# Regression diagnostic statistics
ocir_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model0b_employment_reg_stats)
ocir_prepan_model0b_employment_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment sensitivity model1a sum_score prepan}
# Regression coefficients
ocir_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1a_employment_estimates)
ocir_prepan_model1a_employment_estimates

# Regression diagnostic statistics
ocir_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1a_employment_reg_stats)
ocir_prepan_model1a_employment_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_employment_estimates)
ocir_prepan_model1b_employment_estimates

# Regression diagnostic statistics
ocir_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_employment_reg_stats)
ocir_prepan_model1b_employment_reg_stats
```
